---
title: "Random Stats of Blowjob 2012-2015: Maps"
output: html_document
---

All maps including smaller scale ones not included in [summary](index.html). For raw stats on every individual matched location, see [all locations stats](report-all-locations.html).

```{r, echo=FALSE}
library(proto)
library(gsubfn)
library(DBI)
library(RSQLite)
library(sqldf)
library(knitr)
library(maps)
library(mapdata)

con = dbConnect(SQLite(), dbname='reds.db')

res = dbSendQuery(con, 'select * from view_location_counts_bj')
l.stats = dbFetch(res, n=-1)

simpleCap = function(x) {
  s = strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "", collapse = " ")
}

locationString = function(type, city, region, region_name, country_name) {
  if(is.element(type, c(1,4,5,6))) {
    if(country_name == 'United States') {
      paste(simpleCap(city), region, country_name, sep = ", ")
    }
    else {
      paste(simpleCap(city), country_name, sep = ", ")
    }
  }
  else if(type == 2) {
    paste(simpleCap(region_name), country_name, sep = ", ")
  }
  else if(type == 3) {
    country_name
  }
}

l.stats$location_name = mapply(locationString, l.stats$type, l.stats$city, l.stats$region, l.stats$region_name, l.stats$country_name)
l.stats$lat=as.numeric(l.stats$lat)
l.stats$lon=as.numeric(l.stats$lon)

l.stats$pop_ratio = l.stats$population / l.stats$total_posts
l.stats$mf_ratio = round(l.stats$m4f_posts / l.stats$f4m_posts,1)
l.stats$mm_ratio = round((l.stats$total_posts - l.stats$m4m_posts) / l.stats$m4m_posts,1)
l.stats$success_ratio = round((l.stats$total_posts - l.stats$success_posts) / l.stats$success_posts,1)
```

Maps
=====

Area of circles is directly proportional to total number of posts for that location (hence why they all overlap on world map. See other maps for more detail). The smallest circles are for a location with a single post.

'City' means posts specifying a certain city or local area, 'Region' means posts specifying a broad area (region, US state, UK county etc.), 'Country' is for posts specifying a whole country.

I just realised this map still has the Soviet Union! Sorry Latvia...

World
------

```{r, echo=FALSE, out.width='900px'}
world_map = map('worldHires')
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')), pch=20,cex=l.stats$total_posts^(1/2) / 10)
legend(title='World', x=-170, y=1, legend=c('City','Region','Country'), fill=c('red','blue','#29C326'))
```

Europe
------

```{r, echo=FALSE, out.width='900px'}
europe_map = map('worldHires', xlim=c(-11,50), ylim=c(36,65))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)
legend(title='Europe', x=28, y=54.7, legend=c('City','Region','Country'), fill=c('red','blue','#29C326'))

nw_europe_map = map('worldHires', xlim=c(-11,12), ylim=c(47,59.5))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)
```

North America
---------------

```{r, echo=FALSE, out.width='900px'}
north_america_map = map('worldHires', xlim=c(-130,-60), ylim=c(15,52))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)
legend(title='North America', x=-130.4, y=26.3, legend=c('City','State / Region','Country'), fill=c('red','blue','#29C326'))

ne_us_map = map('worldHires', xlim=c(-79,-70), ylim=c(37,42.5))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)

se_us_map = map('worldHires', xlim=c(-85,-70), ylim=c(25,36))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)

midwest_map = map('worldHires', xlim=c(-95,-78), ylim=c(37.4,50))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)

california_map = map('worldHires', xlim=c(-124,-115), ylim=c(32,39))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')),pch=20,cex=l.stats$total_posts^(1/2) / 10)
```

Asia and Australasia
--------------------

```{r, echo=FALSE, out.width='900px'}
asia_aus_map = map('worldHires', xlim=c(66,180), ylim=c(-47,45))
points(l.stats$lon,l.stats$lat,col=ifelse(l.stats$type == 1 | l.stats$type == 6, 'red',ifelse(l.stats$type==2, 'blue', '#29C326')), pch=20,cex=l.stats$total_posts^(1/2) / 10)
legend(title='Asia & Aus', x=65, y=-7, legend=c('City','Region','Country'), fill=c('red','blue','#29C326'))
```
